Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2017-03-24 paper/presentation/DASFAA_presentation.tex
finish the example, [todo] add the explain to the example

@@

\begin{frame}
\frametitle{How about existing methods? (2/2)}
Event detection methods \textit{by leveraging extra information}
\begin{enumerate}
	\item typical one: Twevent[Li, CIKM 2012]
	\begin{itemize}
		\item divides the tweet into segments according to the Microsoft Web N-Gram service and Wikpedia
		\item detects the bursty segments and cluster these segments into candidate events
		\item still have to trade off between precision and recall
	\end{itemize}
\end{enumerate}
\end{frame}

%------------------------------
%page 6
\begin{frame}
\frametitle{An Example}	
\begin{figure}[h]
		\setlength{\abovecaptionskip}{0.cm}
        \setlength{\belowcaptionskip}{0.cm}
        \centering
        \includegraphics[width=1.0\columnwidth]{../img/hood.pdf}
        \caption{The comparison of the time series between the raw word \textit{hood} and the \textit{Military} related word \textit{hood}, computed on the \textit{Edinburgh twitter corpus}. The rise of document frequency on July 28th, 2011 is corresponding to the event mentioned in \url{https://en.wikipedia.org/wiki/Fort_Hood\#2011_attack_plot}.}
        \label{fig:hood}
\end{figure}
\end{frame}

>>>>

%used for aligning the figure to left
\usepackage[export]{adjustbox}

@@

\begin{frame}
\frametitle{How about existing methods? (2/2)}
Event detection methods \textit{by leveraging extra information}
\begin{enumerate}
	\item typical one: Twevent[Li, CIKM 2012]
	\begin{itemize}
		\item divides the tweet into segments according to the Microsoft Web N-Gram service and Wikpedia
		\item detects the bursty segments and cluster these segments into candidate events
		\item still has to trade off between precision and recall
	\end{itemize}
\end{enumerate}
\end{frame}

%------------------------------
%page 6
\begin{frame}
Much easier to detect the event on the time series of word "hood" related to \textit{Military}.
\frametitle{An Example}	
\begin{figure}[h]
		\setlength{\abovecaptionskip}{0.cm}
        \setlength{\belowcaptionskip}{0.cm}
        \centering
        \includegraphics[width=1.0\columnwidth]{../img/hood.pdf}
        \caption{The comparison of the time series between the raw word \textit{hood} and the \textit{Military} related word \textit{hood}, computed on the \textit{Edinburgh twitter corpus}. Refer the event to \url{https://en.wikipedia.org/wiki/Fort_Hood\#2011_attack_plot}.}
        \label{fig:hood}
\end{figure}

\begin{figure}[h]
		\setlength{\abovecaptionskip}{0.cm}
        \setlength{\belowcaptionskip}{0.cm}
        \centering
        \includegraphics[width=0.5\columnwidth, left]{Fort_Hood.pdf}
\end{figure}
\end{frame}
